%% -*- Mode: LaTeX -*-
%%
%% remotes.tex
%% Created Wed Nov 18 15:00:41 AKST 2015
%% Copyright (C) 2015 by Raymond E. Marcil <marcilr@gmail.com>
%%
%% Remotes
%%

%% ========================= Remotes =============================
%% ========================= Remotes =============================
\newpage
\subsection{Remotes}
``To be able to collaborate on any Git project, you need to know
how to manage your remote repositories.  Remote repositories are
versions of your project that are hosted on the Internet or
network somewhere.  You can have several of them, each of which
generally is either read-only or read/write for you.
Collaborating with others involves managing these remote
repositories and pushing and pulling data to and from them when
you need to share work.  Managing remote repositories includes
knowing how to add remote repositories, remove remotes that are no
longer valid, manage various remote branches and define them as
being tracked or not, and more. In this section, we'll cover some
of these remote-management skills.''\footnote{Git Basics - Working
with Remotes,\\
\href{http://git-scm.com/book/en/v2/Git-Basics-Working-with-Remotes}{http://git-scm.com/book/en/v2/Git-Basics-Working-with-Remotes}}


%% ================== Remote Repositories ========================
%% ================== Remote Repositories ========================
\subsubsection{Remote Repositories}
GitHub's collaborative approach to development depends on
publishing commits from your local repository for other people to
view, fetch, and update.\footnote{About remote repositories,
\href{https://help.github.com/articles/about-remote-repositories/}{https://help.github.com/articles/about-remote-repositories/}}
\\
\\
A remote URL is Git's fancy way of saying ``the place where your
code is stored.'' That URL could be your repository on GitHub, or
another user's fork, or even on a completely different server.
\\
\\
You can only push to two types of URL addresses:
\\
\\
$>$ An HTTPS URL like \cmd{https://github.com/user/repo.git}\\
$>$ An SSH URL, like \cmd{git@github.com:user/repo.git}\\
\\
Git associates a remote URL with a name, and your default remote is usually called origin.


%% ===================== Remote Commands =========================
%% ===================== Remote Commands =========================
\newpage
\subsubsection{Remote Commands}
\begin{table}[htb]
\begin{center}
\begin{tabular}{|p{.20\textwidth}|p{.70\textwidth}|}\hline
Command&Description\\
\hline
\cmd{remote add}&Add a new remote in the directory your repository is stored at.\\
\cmd{remote set-url}&Change a remote's URL.\\
\cmd{remote rename}&Rename an existing remote.\\
\cmd{remote rm}&Remove a remote URL from your repository.\\
\hline
\end{tabular}
\caption {Remote Commands}
\label{table:remote_commands}
\end{center}
\end{table}

\noindent For further reading see ``\href{http://git-scm.com/book/en/Git-Basics-Working-with-Remotes}{Working with Remotes}''
from the Pro Git book.\footnote{Pro Git book, \href{http://git-scm.com/book/en/Git-Basics-Working-with-Remotes}{http://git-scm.com/book/en/Git-Basics-Working-with-Remotes}}


%% ===================== git remote add =========================
%% ===================== git remote add =========================
\newpage
\subsubsection{git remote add}
To add a new remote, use the \cmd{git remote add} command on the
terminal, in the directory your repository is stored at.\footnote{Adding a remote,
\href{https://help.github.com/articles/adding-a-remote/}{https://help.github.com/articles/adding-a-remote/}}
\\
\\
The \cmd{git remote add} command takes two arguments:
\vspace{-10pt}
\begin{verbatim}
$ git remote add <NAME> <REMOTE_URL> 
\end{verbatim}

\noindent Where:
\vspace{-10pt}
\begin{table}[htb]
%%\begin{table}
\begin{center}
\begin{tabular}{p{.20\textwidth}p{.80\textwidth}}
\hspace{20pt}\cmd{<NAME>}&- A remote name, for example, \cmd{origin}\\
\hspace{20pt}\cmd{<REMOTE\_URL>}&- A remote URL, for example, \cmd{https://github.com/user/repo.git}\\
\end{tabular}
\label{table:remote_add}
\end{center}
\end{table}

\vspace{-20pt}
\noindent Git associates a remote URL with a name, and your
default remote is usually called origin.\footnote{About remote repositories,
\href{https://help.github.com/articles/about-remote-repositories/}{https://help.github.com/articles/about-remote-repositories/}}
\\

%% ======================== Examples ============================
%% ======================== Examples ============================
\vspace{10pt}
\noindent \begin{bf}Examples\end{bf}
\begin{Verbatim}
 # This associates the name origin with SSH URL for repo.git repository.
 $ git remote add origin git@github.com:user/repo.git
\end{Verbatim}

\noindent Alternatively using https syntax:

\begin{Verbatim}
 $ git remote add origin https://github.com/user/repo.git
 # Set a new remote

 $ git remote -v
 # Verify new remote
 origin  https://github.com/user/repo.git (fetch)
 origin  https://github.com/user/repo.git (push)
\end{Verbatim}


%% =================== git remote set-url =======================
%% =================== git remote set-url =======================
\newpage
\subsubsection{git remote set-url}
The \cmd{git remote set-url} command changes an existing remote
repository URL.\footnote{Changing a remote's URL,
\href{https://help.github.com/articles/changing-a-remote-s-url/}{https://help.github.com/articles/changing-a-remote-s-url/}}
\\
\\
The git remote set-url command takes two arguments:
\\
$>$ An existing remote name. For example, \cmd{origin} or \cmd{upstream} are two common choices.\\
$>$ A new URL for the remote. For example:\\

\noindent\hspace*{10pt}$>$ If you're updating to use HTTPS, your URL might look like:\\
\noindent\hspace*{23pt}\cmd{https://github.com/USERNAME/OTHERREPOSITORY.git}\\
\\
\noindent\hspace*{10pt}$>$ If you're updating to use SSH, your URL might look like:\\
\noindent\hspace*{23pt}\cmd{git@github.com:USERNAME/OTHERREPOSITORY.git}


%% ========= Switching remote URLs from SSH to HTTPS ===========
%% ========= Switching remote URLs from SSH to HTTPS ===========
\subsubsection{Switching remote URLs from SSH to HTTPS}
\begin{enumerate}
  \item{Open Terminal (for Mac and Linux users) or the command prompt
       (for Windows users).\footnote{Switching remote URLs from HTTPS to SSH,
       \href{https://help.github.com/articles/changing-a-remote-s-url/}{https://help.github.com/articles/changing-a-remote-s-url/}}}
  \item{Change the current working directory to your local project.}
  \item{List your existing remotes in order to get the name of the remote you want to change.
\begin{Verbatim}
 $ git remote -v
 # origin  git@github.com:USERNAME/REPOSITORY.git (fetch)
 # origin  git@github.com:USERNAME/REPOSITORY.git (push)
\end{Verbatim}
       }
  \item{Change your remote's URL from SSH to HTTPS with the git remote set-url command.
\begin{Verbatim}
 $ git remote set-url origin \
 https://github.com/USERNAME/OTHERREPOSITORY.git
\end{Verbatim}
      }

  \item{Verify that the remote URL has changed.
\begin{Verbatim}
$ git remote -v
# Verify new remote URL
# origin  https://github.com/USERNAME/OTHERREPOSITORY.git (fetch)
# origin  https://github.com/USERNAME/OTHERREPOSITORY.git (push)
\end{Verbatim}
       }
\end{enumerate}


%% ========= Switching remote URLs from HTTPS to SSH ===========
%% ========= Switching remote URLs from HTTPS to SSH ===========
\newpage
\subsubsection{Switching remote URLs from HTTPS to SSH}
\begin{enumerate}
  \item{Open Terminal (for Mac and Linux users) or the command prompt
       (for Windows users).\footnote{Switching remote URLs from HTTPS to SSH,
       \href{https://help.github.com/articles/changing-a-remote-s-url/}{https://help.github.com/articles/changing-a-remote-s-url/}}}
  \item{Change the current working directory to your local project.}
  \item{List your existing remotes in order to get the name of the remote you want to change.
\begin{Verbatim}
 $ git remote -v
 origin  https://github.com/USERNAME/REPOSITORY.git (fetch)
 origin  https://github.com/USERNAME/REPOSITORY.git (push)
\end{Verbatim}
       }
  \item{Change your remote's URL from HTTPS to SSH with the git remote set-url command.
\begin{Verbatim}
 $ git remote set-url origin \
 git@github.com:USERNAME/OTHERREPOSITORY.git
\end{Verbatim}
      }

  \item{Verify that the remote URL has changed.
\begin{Verbatim}
 $ git remote -v
 # Verify new remote URL
 origin  git@github.com:USERNAME/OTHERREPOSITORY.git (fetch)
 origin  git@github.com:USERNAME/OTHERREPOSITORY.git (push)
\end{Verbatim}
       }
\end{enumerate}


%% ==================== git remote rename ======================
%% ==================== git remote rename ======================
\subsubsection{git remote rename}
Use the git remote rename command to rename an existing remote.\footnote{Renaming a remote,
\href{https://help.github.com/articles/renaming-a-remote/}{https://help.github.com/articles/renaming-a-remote/}}
\\
\\
The git remote rename command takes two arguments:
\\
\\
$>$ An existing remote name, for example, origin A new name for the\\
$>$ remote, for example, destination

\newpage
\noindent \begin{bf}Example\end{bf}\\
The examples below assume you're cloning using HTTPS, which is recommended.

\begin{Verbatim}
 $ git remote -v
 # View existing remotes
 origin  https://github.com/OWNER/REPOSITORY.git (fetch)
 origin  https://github.com/OWNER/REPOSITORY.git (push)

 $ git remote rename origin destination
 # Change remote name from 'origin' to 'destination'

 $ git remote -v
 # Verify remote's new name
 destination  https://github.com/OWNER/REPOSITORY.git (fetch)
 destination  https://github.com/OWNER/REPOSITORY.git (push)
\end{Verbatim}


%% ====================== git remote rm ======================
%% ====================== git remote rm ======================
\subsubsection{git remote rm}
Use the \cmd{git remote rm} command to remove a remote URL
from your repository.\footnote{Removing a remote,
\href{https://help.github.com/articles/removing-a-remote/}{https://help.github.com/articles/removing-a-remote/}}
\\
\\
The \cmd{git remote rm} command takes one argument:
\\
\\
$>$ A remote name, for example, destination
\\
\\
\noindent \begin{bf}Example\end{bf}
\\
\\
The examples below assume you're cloning using HTTPS, which is recommended.

\begin{Verbatim}
 $ git remote -v
 # View current remotes
 origin  https://github.com/OWNER/REPOSITORY.git (fetch)
 origin  https://github.com/OWNER/REPOSITORY.git (push)
 destination  https://github.com/FORKER/REPOSITORY.git (fetch)
 destination  https://github.com/FORKER/REPOSITORY.git (push)

 $ git remote rm destination
 # Remove remote
 $ git remote -v
 # Verify it's gone
 origin  https://github.com/OWNER/REPOSITORY.git (fetch)
 origin  https://github.com/OWNER/REPOSITORY.git (push)
\end{Verbatim}

\noindent Note: \cmd{git remote rm} does not delete the remote
repository from the server.  It simply removes the remote and
its references from your local repository.
