%% -*- Mode: LaTeX -*-
%%
%% remotes.tex
%% Created Wed Nov 18 15:00:41 AKST 2015
%% Copyright (C) 2015 by Raymond E. Marcil <marcilr@gmail.com>
%%
%% Remotes
%%

%% ========================= Remotes =============================
%% ========================= Remotes =============================
\newpage
\section{Remotes}
``To be able to collaborate on any Git project, you need to know
how to manage your remote repositories.  Remote repositories are
versions of your project that are hosted on the Internet or
network somewhere.  You can have several of them, each of which
generally is either read-only or read/write for you.
Collaborating with others involves managing these remote
repositories and pushing and pulling data to and from them when
you need to share work.  Managing remote repositories includes
knowing how to add remote repositories, remove remotes that are no
longer valid, manage various remote branches and define them as
being tracked or not, and more. In this section, we'll cover some
of these remote-management skills.''\footnote{Git Basics - Working
with Remotes,\\
\href{http://git-scm.com/book/en/v2/Git-Basics-Working-with-Remotes}{http://git-scm.com/book/en/v2/Git-Basics-Working-with-Remotes}}
\\
\\
A remote URL is Git's fancy way of saying ``the place where your
code is stored.'' That URL could be your repository on GitHub, or
another user's fork, or even on a completely different server.\footnote{About remote repositories,
\href{https://help.github.com/articles/about-remote-repositories/}{https://help.github.com/articles/about-remote-repositories/}}
\\
\\
Git associates a remote URL with a name, and your default 
remote is usually called \cmd{origin}.\footnote{Ibid.}\\
\\
\noindent A remote repository provides easy access from distributed
locations and alleviates backup issues.  Candidates for
a remote repositories include Bitbucket,\footnote{Bitbucket - Code, Manage, Collaborate,
Bitbucket is the Git solution for professional teams\\
\href{https://bitbucket.org/}{https://bitbucket.org/}}
GitHub,\footnote{GitHub - Where software is built\\
\href{https://github.com/}{https://github.com/}}
or Google Code.\footnote{Google Code - Provides a free collaborative development environment
for open source projects.\\
\href{https://code.google.com/}{https://code.google.com/}}

%%\input{remotes/cloud/github/github.tex}


%% Remote Commands
\input{remotes/commands/commands.tex}
